### 2014-07-28 paper/paper.tex
Added the biginnings of a bibliography to the paper
Added most of the documents that I read for the bibliography. Also Started on the approch

\documentclass[12pt]{article}
\usepackage{enumerate}
\usepackage{courier}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{setspace}

@@

@@

@@

>>>>

\documentclass[12pt]{article}
\usepackage{enumerate}
\usepackage{courier}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{setspace}
\usepackage[numbers]{natbib}

@@

Quite a bit of research has been done in the field of sentiment analysis
recently. Much of the work has involved data from other contexts such as Movie
reviews \cite{Pang2002}, and blog posts \cite{Melville2009}. The challenges
associated with classifying Twitter data has attracted researchers in the past
few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.

@@

The Maximum Entropy classification method that was focused on due to the
limited duration of the project. This supervised machine learning method
calculates the probability that a given document $d$ belongs to the class $c$.

The maximum entropy approach is well described in \cite{Pang2002} and
\cite{Nigam1999} and is summarized below.

\begin{equation}
    P(c | d) = \frac{1}{Z(d)} exp( \sum\limits_{i} \lambda _{i,c} F_{i,c}(d,c) )
\end{equation}

Where $Z(d)$ is a normalization function. $F_{i,c}$ is a feature function for
feature $f_{i}$ and class $c$.

@@

\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{paper}
